---
title: "Reveal.js Example"
author: "Maikel Verouden"
date: "`r Sys.Date()`"
output: 
  revealjs::revealjs_presentation:
    theme: default
    highlight: kate
    center: false
    transition: none
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details --- on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

This is text with an equation: $$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

## Fade in, Slide out {data-transition="fade-in slide-out"}

What happens?

## Slide in, Fade out {data-transition="slide-in fade-out"}

And here?

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

# Horizontal Slide 1

Horizontal with the possibility to go vertical

## Vertical Slide 1

Vertigo 1

## Vertical Slide 2

Vertigo 2

# Horizontal Slide 2

Continue horizontal
